Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-28 colt-21/cvx-flats.tex
first paragraph and abstract

\begin{abstract}
  Given a prediction task, it is crucial to understand when one can and cannot design an ``efficient'' consistent convex surrogate loss.
  The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
  Techniques to design and analyze surrogate losses in these scenarios are typically studied by different frameworks.%: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
We unify these settings by generalizing notions of consistency from machine learning and give lower bounds on prediction dimension that extend across settings.
Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
For statistic estimation, our lower bound gives new results for estimating variance, entropy, and norms of the conditional distribution, and resolves stated open problems in the literature.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

\section{Introduction}\label{sec:intro}
%supervised learning blah
Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous prediction problems when one seeks to estimate a target conditional statistic\raft{I felt we needed a sentence like this to justify \emph{why} we need a surrogate. And given that we need it, we can't really avoid hinting at the quadrants...}.
In both of these settings, we minimally require \emph{consistency}, a precursor to excess risk bounds and rates.
Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
the target risk is also minimized, or the continuous prediction approaches the true conditional statistic.

>>>>

\begin{abstract}
Given a prediction task, we wish to understand when one can and cannot design an ``efficient'' consistent convex surrogate loss.
The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
These two scenarios typically have involved quite different techniques for designing and analyzing surrogate losses.
We unify these settings by generalizing notions of consistency from machine learning and give lower bounds on prediction dimension that extend across settings.
Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
For statistic estimation, our lower bound gives new results for estimating variance, entropy, and norms of the conditional distribution, resolving some open problems.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

\section{Introduction}\label{sec:intro}
%supervised learning blah
A surrogate loss function is an error measure that one optimizes, that is related but not identical to one's target problem of interest.
Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
There are two main reasons why a surrogate loss is necessary: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the goal is to estimate some target statistic rather than a target loss, as in many continuous estimation problems.
%(1) often occurs in discrete settings such as classification, while (2) is commone in continuous prediction problems when one seeks to estimate a target conditional statistic.%\raft{I felt we needed a sentence like this to justify \emph{why} we need a surrogate. And given that we need it, we can't really avoid hinting at the quadrants...}
In both settings, one minimally requires \emph{consistency}, a precursor to excess risk bounds and convergence rates.
Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest, i.e. (1) the target risk is also minimized, or (2) the continuous prediction approaches the true conditional statistic.
